### 2018-03-17 Sections/physical_architectures_for_quantum_computing.tex
Bloch sphere, dyn dec
CV encoding
QW fig

We will briefly summarise the discrete-time QW model, as it most readily lends itself to linear optics implementation, and illustrate the parallels with \textsc{BosonSampling}. First, let us consider the standard simple example scenario of a single quantum walker, on a linear graph topology, using a Hadamard coin\index{Hadamard gate},
\begin{align}
\hat{C} = \frac{1}{\sqrt{2}}\begin{pmatrix}1 & 1 \\
1 & -1
\end{pmatrix},
\end{align}
which has been experimentally demonstrated using both bulk-optics \cite{bib:Broome10} and time-bin encoding \cite{bib:Schreiber10, bib:RohdeQWExp12}. The walker is defined by two Hilbert spaces: the position $x$, and the coin {$c=\pm 1$}, where $+1$ ($-1$) indicates that the walker is moving to the right (left). The basis states are then $\ket{x,c}$, and the state of the walker takes the form,
\begin{align}
\ket\psi = \sum_{x,c} \lambda_{x,c} \ket{x,c}.
\end{align}
The evolution of the walk is given by the coin and step operators,
\begin{align} \index{Coin operators}\index{Step operators}
\hat{C}\ket{x,\pm 1} &\to \frac{1}{\sqrt{2}}(\ket{x,+1}\pm \ket{x,-1}), \nonumber \\
\hat{S}\ket{x,c} &\to \ket{x+c,c}.
\end{align}
The Hadamard coin operator could be replaced with any arbitrary $\text{SU}(2)$ matrix. The total time-evolution of the walk is then given by,
\begin{align}
\ket{\psi(t)} = (\hat{S}\hat{C})^t\ket{\psi(0)},
\end{align}
where \mbox{$t\in\mathbb{Z}_+$}. Upon measurement, the probability of the walker being at position $x$ is simply given by summing the probabilities over the coins at a given position,
\begin{align}
P(x) = |\lambda_{x,-1}|^2 + |\lambda_{x,+1}|^2.
\end{align}

@@

\comment{Add fig for classical vs quantum discrete-time walk}

@@

Squeezing simply corresponds to a dilation along a particular axis in phase-space. Squeezing is represented using the squeezing operator\index{Squeezing operator},
\begin{align}
\hat{S}(\xi) = \text{exp}\left[ \frac{1}{2}(\xi^*\hat{a}^2 - \xi{\hat{a}^{\dag 2}})\right],
\end{align}
where \mbox{$\xi  = r e^{i \varphi}$}, $r$ is known as the squeezing parameter, which will determine the size of the squeezing and \mbox{$\varphi \in [0, 2\pi]$} denotes that axis along which the squeezing is taking place.

@@

In the position/momentum picture, the logical generalisations of the Pauli $\hat{X}$ and $\hat{Z}$ qubit gates may be thought of as displacements (Sec.~\ref{sec:non_lin_opt}) in the real and imaginary directions in phase-space \cite{bib:KokLovettBook},
\begin{align}
\hat{X}(s) \equiv \hat{D}(s)	, \, s\in\mathbb{R},\nonumber\\
\hat{Z}(t) \equiv \hat{D}(it), \, t\in\mathbb{R},
\end{align}
where,
\begin{align}
\hat{D}(\alpha) = \text{exp}\left[\alpha\hat{a}^\dag - \alpha^*\hat{a}\right],
\end{align}
is the phase-space displacement operator\index{Displacement operator}.

>>>>

We will briefly summarise the discrete-time QW model, as it most readily lends itself to linear optics implementation, and illustrate the parallels with \textsc{BosonSampling}. First, let us consider the standard simple example scenario of a single quantum walker, on a linear graph topology, using a Hadamard coin\index{Hadamard gate},
\begin{align}
\hat{C} = \frac{1}{\sqrt{2}}\begin{pmatrix}1 & 1 \\
1 & -1
\end{pmatrix},
\end{align}
which has been experimentally demonstrated using both bulk-optics \cite{bib:Broome10} and time-bin encoding \cite{bib:Schreiber10, bib:RohdeQWExp12}. The walker is defined by two Hilbert spaces: the position $x$, and the coin {$c=\pm 1$}, where $+1$ ($-1$) indicates that the walker is moving to the right (left). The basis states are then $\ket{x,c}$, and the state of the walker takes the form,
\begin{align}
\ket\psi = \sum_{x,c} \lambda_{x,c} \ket{x,c}.
\end{align}
The evolution of the walk is given by the coin and step operators,
\begin{align} \index{Coin operators}\index{Step operators}
\hat{C}\ket{x,\pm 1} &\to \frac{1}{\sqrt{2}}(\ket{x,+1}\pm \ket{x,-1}), \nonumber \\
\hat{S}\ket{x,c} &\to \ket{x+c,c}.
\end{align}
The Hadamard coin operator could be replaced with any arbitrary $\text{SU}(2)$ matrix. The total time-evolution of the walk is then given by,
\begin{align}
\ket{\psi(t)} = (\hat{S}\hat{C})^t\ket{\psi(0)},
\end{align}
where \mbox{$t\in\mathbb{Z}_+$}. Upon measurement, the probability of the walker being at position $x$ is simply given by summing the probabilities over the coins at a given position,
\begin{align}
P(x) = |\lambda_{x,-1}|^2 + |\lambda_{x,+1}|^2.
\end{align}
An example of this kind of quantum walk is shown in Fig.~\ref{fig:QW_ev}.

\begin{figure}[!htb]
\includegraphics[width=0.47\textwidth]{quantum_walk_evolution}
\caption{Evolution on a 1D quantum walk on a line with a Hadamard coin operator. The walker begins localised at the origin and then spreads out as a superposition over the position space ($x$) with time ($t$). A key feature of this distribution is that its variance grows quadratically with time, compared with linear growth for the equivalent classical random walk. This enhanced spreading forms the basis of the quantum walk search algorithm, with quadratic enhancement compared to a classical search.} \label{fig:QW_ev}
\end{figure}

@@

@@

Squeezing simply corresponds to a dilation along a particular axis in phase-space. Squeezing is represented using the squeezing operator\index{Squeezing operator},
\begin{align}\label{eq:sq_op}
\hat{S}(\xi) = \text{exp}\left[ \frac{1}{2}(\xi^*\hat{a}^2 - \xi{\hat{a}^{\dag 2}})\right],
\end{align}
where \mbox{$\xi  = r e^{i \varphi}$}, $r$ is known as the squeezing parameter, which will determine the size of the squeezing and \mbox{$\varphi \in [0, 2\pi]$} denotes that axis along which the squeezing is taking place.

@@

In the position/momentum picture, the logical generalisations of the Pauli $\hat{X}$ and $\hat{Z}$ qubit gates may be thought of as displacements (Sec.~\ref{sec:non_lin_opt}) in the real and imaginary directions in phase-space \cite{bib:KokLovettBook},
\begin{align}
\hat{X}(s) \equiv \hat{D}(s)	, \, s\in\mathbb{R},\nonumber\\
\hat{Z}(t) \equiv \hat{D}(it), \, t\in\mathbb{R},
\end{align}
where,
\begin{align}\label{eq:disp_op}
\hat{D}(\alpha) = \text{exp}\left[\alpha\hat{a}^\dag - \alpha^*\hat{a}\right],
\end{align}
is the phase-space displacement operator\index{Displacement operator}.
